FlowFPX: Nimble Tools for Debugging Floating-Point Exceptions

### 2023-06-07 paper.tex
Add section to discussion, round out shallow waters section

%% --- autogenerated TOC ---
% juliacon
% document
%   Introduction
%   To Kill a Floating Point
%     Where do NaNs come from?
%     NaN kills
%   FloatTracker Internals
%     Catching NaN kills
%     NaN propagation monitoring
%     NaN injection
%   Case Studies
%     Surprise NaNs: ShallowWaters
%     NaN fuzzing to find a kill: OrdinaryDiffEq
%     NaN Kills: Finch
%     A Bug-Hunting Safari
%   Evaluation
%   Discussion
%   Related Work
%   Acknowledgments
% document
%% --- end autogenerated TOC ---

@@

We can see that the NaN appeared from subtraction (first line) and that it was used in the \texttt{momentum\_u!} function on line 246 of the \texttt{rhs.jl} file (second line).
In figure~\ref{fig:nan-gens} we can tell that this must be the result of $\infty - \infty$.
Where did the $\infty$ come from?

% What do we say here?!

@@

\section{Discussion}

@@

% Local Variables:
% jinx-local-words: "CFL CSTGs Courant Friedrichs JuliaHub Lewy OrdinaryDiffEq ShallowWaters TrackedFloat isnan"
% End:

>>>>

%% --- autogenerated TOC ---
% juliacon
% document
%   Introduction
%   To Kill a Floating Point
%     Where do NaNs come from?
%     NaN kills
%   FloatTracker Internals
%     Catching NaN kills
%     NaN propagation monitoring
%     NaN injection
%   Case Studies
%     Surprise NaNs: ShallowWaters
%     NaN fuzzing to find a kill: OrdinaryDiffEq
%     Finch
%     A Bug-Hunting Safari
%   Evaluation
%   Discussion
%     Tracking more than NaNs
%     Enhanced Fuzzing
%   Related Work
%   Acknowledgments
% document
%% --- end autogenerated TOC ---

@@

We can see that the NaN appeared from subtraction (first line) and that it was used in the \texttt{momentum\_u!} function on line 246 of the \texttt{rhs.jl} file (second line).
In figure~\ref{fig:nan-gens} we can tell that this must be the result of $\infty - \infty$.

Thus, with little effort we were able to track down where the NaNs were originating.
More work is needed to follow the $\infty$ back to wherever \emph{it} came from.
Fortunately, we will be able to extend FloatTracker to handle more than just NaNs---watching and logging \texttt{Inf}s should be completely tractable.
See~\cref{discussion} for more on future plans around this.

% TODO: if we get some handling with Inf working, then we should keep tracing this back.
% Where did the $\infty$ come from?

@@

\section{Discussion}
\label{s:discussion}

\subsection{Tracking more than NaNs}

% This is mostly a stand-in in case we don't get around to adding Inf tracking.
% It should be easy to do, but whether or not we have enough time to do it is
% another matter.
FloatTracker is capable of monitoring all sorts of events in a floating point value's lifetime---not just a value going to NaN.
Extending FloatTracker to handle \texttt{Inf} is just a matter of engineering.
Other values of interest may follow.

@@

% Local Variables:
% jinx-local-words: "CFL CSTGs Courant Friedrichs JuliaHub Lewy OrdinaryDiffEq RxInfer ShallowWaters TrackedFloat isnan"
% End:
